Blockchain in the Industrial Sector

### 2020-05-06 paper.tex
Revision v2

\subsection{Motivation}
Until today, the industry has seen three major revolutions, and the fourth is on its way \cite{Rojko2017}. The fourth industrial revolution (Industry 4.0) represents the next step in the evolution of traditional factories towards smart automated factories. These factories are designed in such a way to reduce production costs, increase productivity, improve quality, and achieve efficient use of resources. To achieve all that a wide range of technologies has to be used in manufacturing processes like Robotics, Autonomous Systems, Internet of Things, Cloud Computing, Intelligent Data Analytics, Artificial Intelligence and many more \cite{Fernandez-carames2018}.

@@

\noindent However, all these technologies are relying on centralized networks and need to trust middlemen and third-party operators \cite{Angrish2018a,Sikorski2017,Li2018,Afanasev2018,Garrocho2019}. The result, manufacturing industry facing many challenges related to the data. Challenges like transparency, security, privacy, and trustworthiness of the data. These challenges stand in the way of Industry 4.0 reaching its full potential. A common and trusted platform is needed to facilitate the relationships between parties across the value chain. These challenges can be overcome by using blockchain technologies.

@@

\noindent The main advantage of the blockchain is that it is a distributed shared ledger instead of a traditional centralized system \cite{Zheng2017}. It enabled a group of entities who don’t trust each other to reach an agreement on a certain activity and register it without the need for a middleman or third party. The agreed-upon activity can be anything like payment transactions, purchase activity, or any non-financial transaction \cite{Mohamed}. The great revolution blockchain brought by creating an immutable, secure and transparent system to log and execute any type of transaction. Blockchain can also preserve the order of events and ensure the correctness of logged transactions over time. No one can individually delete or modify any of the recorded transactions. Also, the invention of smart contracts made the blockchain a promising platform for developing distributed and trustworthy applications \cite{Mohamed}. As a result, many industries and businesses are considering its utilization and more research is being done to effectively apply blockchain in their domains.

@@

\noindent Given its key features such as immutability, traceability, and reliability of the information, it represents a perfect candidate to be integrated into the industrial plants. It will increase its efficiency, security, and provenance concerning the related data of goods, assets, and operations \cite{Internet2019}. In addition, they enable the creation of new business models that were impossible to form a few years ago. With the introduction of blockchain, businesses and individuals can record and secure their conducted agreements among themselves without middle parties.

\subsection{Problem Statement}
In the manufacturing industry, many technologies are evolving. They all have the same goal which is to increase the efficiency, capability, and adaptability of the manufacturing systems. However, all technologies rely on a centralized network provided by a third party. This limits the ability of these technologies to achieve their goal and make the manufacturing systems not scalable. Also, this imposes vulnerabilities as cyber-attacks and security problems.

\subsection{Research Purpose and Questions}
The aim of this thesis is to shed light on the blockchain’s capability to improve the manufacturing industry. The thesis will investigate the feasibility of implementing blockchain solutions within the boundaries of smart factories. To understand how blockchain can work with other technologies to overcome the challenges mentioned earlier. The main question for this research is:

@@

\subsection{Outline}
The remainder of the document is structured as follows. Section 2 presents an overview of the research that has been made in the fields of blockchain for the manufacturing industry. In the next section, we provide an overview of the system requirements and functionalities. Then section 4, details some technical details about the proposed system implementation. Later in section 5, a short section about the system evaluation. Finally, the last section summarizes the document.

@@

\subsection{Summery}
It is evident from the works we discussed in this section that researchers have already presented some applications of blockchain in the manufacturing industry. The approaches as we saw vary wildly and each work looks at the problem from a different angle. Some of the works focused on the horizontal integration between manufacturing parties to enable the concept of manufacturing as a service. Either between manufacturers themselves or between manufacturers and customers. These works neglected the actual manufacturing process and focused more on the concept of trading. On the other hand, some works discussed the manufacturing process by enabling machine-to-machine communication over the blockchain. However, the use cases of these works were oversimplified and in most cases were limited in size (two machines). This does not reflect the actual communications between machines on a production line.

\section{Proposed Solution}
To answer the research questions, we will try to build a blockchain-based system in the area of manufacturing. The system collects, stores and manages the key information generated by the factory infrastructure. The focus is on both the machines and the products being manufactured. For products, it provides the ability to track and trace each product throughout a production pipeline. Tracking the machines includes the status of the machines at any point in time. The system enables also the autonomous machine-to-machine communications. Where one machine can ask another machine to perform a certain task without any human involvement. The system envisioned will be designed and implemented using smart contract technologies and blockchain. It will be decentralized and distributed. The system will be serving the entities participating in the manufacturing industry such as suppliers, manufacturers, and customers.

@@

\noindent Each machine and product has a digital profile. The profile of the product contains all related information about how the product has been manufactured. The profile will contain the full log of all the industrial tasks performed to a product. This includes the machines information performed the tasks and the timestamps. Each product will have an information tag attached to it to serve as a digital identity. This can be a bardcode or RFID. This tag will serve as an identifier linking the physical product with its virtual twin on the network. Also the machines will have a digital profile. The profile of the machine will contain related information about the industrial tasks performed by this machine. All the data in the network is stored on a blockchain and is available to anyone running the system software with a correct authentication.

@@

\newpage
\section{Implementation}
The figure \ref{fig:system_overview} shows a high-level overview of the system compounds. The system consists of two main parts. The blockchain part, which is a private permissioned blockchain with a set of deployed smart contracts. The factory part is the infrastructure of the factory with all the machines and sensors. These two parts are communicating using Message Queuing Telemetry Transport (MQTT) protocol through the MQTT broker. MQTT is an open message protocol that enables the transmission of data in the form of messages between devices. The following sub-sections will explain each compound in details.

@@

\subsection{Factory Infrastructure}
This includes different types of the manufacturing resources like machines and sensors. We assume that all the resources are able to communicate using MQTT protocol. Each resource can send and receive messages with a certain topic. The messages sent by these resources will be forwarded through the MQTT broker to a web application. Then it will send the corresponding transactions to the blockchain.

@@

\noindent To simulate such infrastructure in our implementation we are using Fischertechnik \footnote{https://www.fischertechnik.de/} factory model. It is a simulation of a factory used for learning and understanding industry 4.0 applications. It depicts the ordering process, the production process and the delivery process in digitised and networked steps \cite{Industry}. It consists of several modules like storage and retrieval stations, vacuum suction grippers, high-bay warehouse, multi-processing station with kiln, sorting line with color detection, environmental sensor, and pivoting camera. The modules are managed by six controllers. All of them networked within the factory and communicate with each other via MQTT.

\subsection{MQTT Broker}
An MQTT broker receives the messages from the factory and forwards it into the web application. In the actual implementation we will use the broker provided by the Node-RED server \footnote{https://nodered.org/} but any other broker can be used.

\subsection{Front-End Web Application}
This is just a front end application used to communicate with the blockchain. It can be hosted locally or in the cloud. The application uses standard front end technologies to build the user interfaces. To interact with the blockchain, it will use the Web3.js library \footnote{https://github.com/ethereum/web3.js/}. It is an Ethereum Javascript API implements the JSON-RPC protocol to connect and interact with any Ethereum blockchain networks. This application servers two proposes. The first one is to act like broker between the blockchain and the MQTT broker as the former can not connect directly to the blockchain. The second is to allow the actors to interact with the system and access the information.

\subsection{Truffle Framework}
We are using Truffle \footnote{https://github.com/trufflesuite/truffle} as development framework. Truffle is a development environment, testing framework and asset pipeline for Ethereum. It allows easy compiling, deploying, and testing of smart contracts written in Solidity. Truffle is built on the top of web3.js and provides many functionalities. This framework will be used to deploy the smart contracts into the blockcain. Also, it will be used to deploy the web3.js code of the web application.

\subsection{Quorum Blockchain}
For the implementation of this thesis we are using the Quorum \footnote{https://www.goquorum.com/} blockchain. It is a permissioned implementation of Ethereum. It has several advantages over the public Ethereum like privacy, high performance, and support multiple consensus algorithms. As Ethereum, Quorum uses standard Solidity for writing smart contracts.

@@

\section{Conclusion}

>>>>

\subsection{Motivation}
Until today, the industry has seen three major revolutions, and the fourth is on its way \cite{Rojko2017}. The fourth industrial revolution (Industry 4.0) represents the next step in the evolution of traditional factories towards smart automated factories. These factories are designed in such a way to reduce production costs, increase productivity, improve quality, and achieve efficient use of resources. To achieve all that a wide range of technologies have to be used in manufacturing processes like Robotics, Autonomous Systems, Internet of Things, Cloud Computing, Intelligent Data Analytics, Artificial Intelligence, and many more \cite{Fernandez-carames2018}.

@@

\noindent However, all these technologies are relying on centralized networks and need to trust middlemen or third-party operators \cite{Angrish2018a,Sikorski2017,Li2018,Afanasev2018,Garrocho2019}. As a result, the industry is facing many challenges related to the data. Challenges like transparency, security, privacy, and trustworthiness. These challenges prevent Industry 4.0 to reach its full potential. A decentralized and trusted platform is needed to facilitate the relationships among parties across the value chain. Such a platform can be built with the help of blockchain technologies.

@@

\noindent The main  advantage of the blockchain is decentralization. It is a distributed shared ledger instead of the traditional centralized systems \cite{Zheng2017}. It enables a group of entities to reach an agreement on a certain activity and register it without the need for a middleman or third party. The agreed-upon activity can be anything like payment transactions, purchase activity, or any non-financial transaction \cite{Mohamed}. The great revolution blockchain brought by creating an immutable, secure and transparent system to log and execute any type of transaction. Blockchain can also preserve the order of events and ensure the correctness of logged transactions over time. No one can individually delete or modify any of the recorded transactions. Also, the invention of smart contracts made the blockchain a promising platform for developing distributed and trustworthy applications \cite{Mohamed}. As a result, many industries and businesses are considering its utilization and more research is being done to effectively apply blockchain in their domains.

@@

\noindent Given its key features such as immutability, traceability, and reliability of the information, it represents a perfect candidate to be integrated into the industrial plants. It will increase its efficiency, security, and provenance concerning the related data of goods, assets, and operations \cite{Internet2019}. In addition, these features enable the creation of new business models that were impossible to form a few years ago. With the introduction of blockchain, businesses and individuals can record and secure their conducted agreements among themselves without middle parties.

\subsection{Problem Statement}
In the manufacturing industry, many technologies are evolving. They all have the same goal in increasing the efficiency, capability, and adaptability of the manufacturing systems. However, all technologies rely on a centralized network provided by a third party. This limits the ability of these technologies to achieve their goal and limit the scalability of the manufacturing systems. Also, it imposes vulnerabilities as cyber-attacks and security problems.

\subsection{Research Purpose and Questions}
The aim of this thesis is to shed light on the blockchain’s capability to improve the manufacturing industry. It will investigate the feasibility of implementing blockchain solutions within the boundaries of smart factories. To understand how blockchain can work with other technologies to overcome the challenges mentioned earlier. The main question for this research is:

@@

\subsection{Outline}
The remainder of the document is structured as follows. Section 2 presents an overview of the research that has been made in the fields of blockchain for the manufacturing industry. In the next section, we provide an overview of the system requirements and functionalities. Then section 4, discusses some technical details about the proposed system implementation. Later in section 5, a short section about the system evaluation. Finally, the last section summarizes the document.

@@

\subsection{Summery}
It is evident from the works we discussed in this section that researchers have already presented some applications of blockchain in the manufacturing industry. The approaches as we saw vary wildly and each work looks at the problem from a different angle. Some of the works focused on the horizontal integration between manufacturing parties to enable the concept of manufacturing as a service. Either between manufacturers themselves or between manufacturers and customers. These works neglected the actual manufacturing process and focused more on the concept of trading. On the other hand, some works discussed the manufacturing process by enabling machine-to-machine communication over the blockchain. However, the use cases of these works were oversimplified and in most cases were limited in size (two machines). This does not reflect the actual communications between machines on a production line. The majority of the discussed works did not store information about the manufactured products. To overcome these points, we propose our solution in the next section.

\section{Proposed Solution}
To answer the research questions, we will try to build a blockchain-based system in the area of manufacturing. The system collects, stores, and manages the key information generated by the factory infrastructure. The focus is on both the machines and the products being manufactured. Regarding the products, the system provides the ability to track and trace each product throughout a production pipeline. Regarding the machines, it tracks the status of the machines at any point in time. The system enables also the autonomous machine-to-machine communications. Where one machine can ask another machine to perform a certain task without any human involvement. The system envisioned will be designed and implemented using blockchain technologies such as smart contracts. It will be decentralized and distributed. The system will be serving the entities participating in the manufacturing industry such as suppliers, manufacturers, and customers.

@@

\noindent In the system, each machine and product has a digital profile. The profile of the product contains all related information about how the product has been manufactured. The profile will contain the full log of all the industrial tasks performed to this product. This includes information about the machines performed the tasks and information about the surrounding environment. Each product will have an information tag attached to it to serve as a digital identity. This can be a barcode or RFID. The tag will serve as an identifier linking the physical product with its virtual twin on the network. The profile of the machine will contain related information about the industrial tasks performed by this machine and information about the communication with other machines. All the data in the network is stored on a blockchain and is available to anyone running the system software with correct authentication.

@@

\section{Implementation}
The figure \ref{fig:system_overview} shows a high-level overview of the system compounds. The system consists of two main parts. The blockchain part, which is a private permissioned blockchain with a set of deployed smart contracts. The factory part is the infrastructure of the factory with all the machines and sensors. These two parts are communicating using Message Queuing Telemetry Transport (MQTT) protocol through the MQTT broker. MQTT is an open message protocol that enables the transmission of data in the form of messages between devices. The following sub-sections will explain each compound in detail.

@@

\subsection{Factory Infrastructure}
This includes different types of manufacturing resources like machines and sensors. We assume that all resources are able to communicate using MQTT protocol. Each resource can send and receive messages with a certain topic. The messages sent by resources will be forwarded through the MQTT broker to a web application. Then it will send the corresponding transactions to the blockchain.

@@

\noindent To simulate such infrastructure in our implementation, we are using Fischertechnik \footnote{https://www.fischertechnik.de/} factory model. It is a simulation of a factory used for learning and understanding industry 4.0 applications. It depicts the ordering process, the production process, and the delivery process in digitised and networked steps \cite{Industry}. It consists of several modules like storage and retrieval stations, vacuum suction grippers, high-bay warehouse, multi-processing station with kiln, sorting line with color detection, environmental sensor, and pivoting camera. The modules are managed by six controllers. All of them networked within the factory and communicate with each other via MQTT.

\subsection{MQTT Broker}
An MQTT broker receives the messages from the factory and forwards it to the web application. In the actual implementation, we will use the broker provided by the Node-RED server \footnote{https://nodered.org/} but any other broker can be used.

\subsection{Front-End Web Application}
This is just a front end application used to communicate with the blockchain. It can be hosted locally or in the cloud. The application uses standard front end technologies to build the user interface. To interact with the blockchain, it will use the Web3.js library \footnote{https://github.com/ethereum/web3.js/}. It is an Ethereum Javascript API implements the JSON-RPC protocol to connect and interact with any Ethereum blockchain network. This application servers two proposes. The first one is to act as a broker between the blockchain and the MQTT broker as the former can not connect directly to the blockchain. The second is to allow the actors to interact with the system.

\subsection{Truffle Framework}
This is not an actual active compound of the system. Truffle \footnote{https://github.com/trufflesuite/truffle} is a development framework. Truffle is a development environment, testing framework, and asset pipeline for Ethereum. It allows easy compiling, deploying, and testing of smart contracts written in Solidity. Truffle is built on the top of web3.js and provides many other functionalities. This framework will be used to deploy smart contracts into the blockchain. Also, it will be used to deploy the web3.js code of the web application.

\subsection{Quorum Blockchain}
For the implementation of this thesis we are using the Quorum \footnote{https://www.goquorum.com/} blockchain. It is a permissioned implementation of Ethereum. It has several advantages over public Ethereum like privacy, high performance, and support multiple consensus algorithms. As Ethereum, Quorum uses standard Solidity for writing smart contracts.

@@

\section{Conclusion}
In this document, we presented a proposal for a decentralized tracking system for the manufacturing industry. The system is utilizing blockchain technologies such as smart contracts to overcome the challenges caused by the centralization of traditional manufacturing systems. To be continued...
